Contention Management for 5G

### 2017-02-07 article/article.tex
ltk

\graphicspath{{figures/}}
\newcommand\rmatching{${\cal R}$-matching\xspace}
\newcommand\mdelay{$\cal M$-delay\xspace}
\newcommand\matchedgraph{{\bf matched graph}}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\newcommand{\reporttitle}{Contention management for Deterministic Networking}     % Titre
\newcommand{\reportauthor}{Maël \textsc{Guiraud }} % Auteur
\newcommand{\reportsubject}{Master Thesis} 
\newcommand{\HRule}{\rule{\linewidth}{0.5mm}}
\setlength{\parskip}{1ex} % Espace entre les paragraphes

@@

      A {\bf routing function} $\cal R$ in $G$ associates to each pair of vertices $(u,v)$ a route from $u$ to $v$. Let $\cal C$ be an {\bf assignment} in $G$, i.e., a set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$. \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}

@@

      \begin{center}

      \fbox{\parbox{12cm}{
      Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
      Indeed, consider messages of size 1, we can build a graph, with $c$ routes $r_i \in {\cal R}_{\cal C}, i < c$ which all intersect two by two and
      such that if $r_i$ and $r_j$ have $v$ as first common vertex we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.
      Therefore there is a $2$-periodic affectation by setting all $m_i$ to $0$.

      A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$. The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.

      Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$. The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.

      A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.

      \begin{tabular}{cc}
      \includegraphics[scale=0.5]{Fig5.pdf} & \includegraphics[scale=1]{Fig7.pdf}\\
      $\lambda(v,r_i) - \lambda(v,r_j)=1$ & Conflict graph\\
      \end{tabular}\newline

      On the other hand if we set all $\lambda(v,r_i) - \lambda(v,r_j)=P$, there is no $P$-periodic affectation if $P<l$.

      \begin{tabular}{cc}
      \includegraphics[scale=0.5]{Fig6.pdf} & \includegraphics[scale=1]{Fig8.pdf}\\
      $\lambda(v,r_i) - \lambda(v,r_j)=2$ & Conflict graph\\
      \end{tabular}\newline
      \begin{center}
      Here for P=2, there is no $P$-periodic affectation.
      \end{center}

      Therefore if we choose and odd value for $P$ and $l=P+1$, there is no $P$-periodic affectation but modulo $2$ all $\lambda(v,r_i) - \lambda(v,r_j)$
      are equal to one thus we have a $2$-periodic affectation. 
      }}

      \end{center}
   \subsection{Problems}

@@

@@

    As in the previous proof, a $k$-coloring of $G$ gives a $k$-periodic schedule of $H$
    and conversly. Therefore if we can approximate the value of PRA  within a factor $f$,
    we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
    by doing the previous reduction for all possible $k$. The proof follows from the hardness of approximability
    of finding a minimal coloring~\cite{zuckerman2006linear}.
    \end{proof}

@@

      \Edge(1)(2)
      \Edge(1)(3)
    \node (1) at (-3,4){\Huge $\rightarrow$};
    \end{tikzpicture}

@@

	\IF{$P1[j]$ is free, and the corresponding slot(s) in P2 are free}

>>>>

\graphicspath{{figures/}}
\newcommand\rmatching{${\cal R}$-matching\xspace}
\newcommand\mdelay{$\cal M$-delay\xspace}
\newcommand\matchedgraph{{\bf matched graph}}
\newtheorem{proposition}{Proposition}
\newtheorem{theorem}{Theorem}
\setlength{\parskip}{1ex} % Espace entre les paragraphes

@@

      A {\bf routing function} $\cal R$ in $G$ associates to each pair of vertices $(u,v)$ a route from $u$ to $v$. Let $\cal C$ be an {\bf assignment} in $G$, i.e., a set of couples of different vertices of $G$. We denote by $\cal R_{\cal C}$ the set of routes ${\cal R}(u,v)$ for any $(u,v)$ in $\cal C$. $\cal R_{\cal C}$ is called an {\bf assigned graph}, and contains all the information needed in forthcoming problems (couples of vertices, routes and delay of the arcs).

      \todo{Si on s'en sert, ajouter ici que le routage est cohérent.}

@@

      Notice that the notion of $P$-periodic affectation \textbf{is not monotone} with regard to $P$. 
      Indeed, consider messages of size 1, we can build a graph, with $c$ routes $r_i \in {\cal R}_{\cal C}, i < c$ which all intersect two by two and
      such that if $r_i$ and $r_j$ have $v$ as first common vertex we have $\lambda(v,r_i) - \lambda(v,r_j)=1$.
      Therefore there is a $2$-periodic affectation by setting all $m_i$ to $0$.

%       A {\bf conflict graph} represents the collision between the routes of $ {\cal R}_{\cal C}$. The vertices of a conflict graph $G = (V,E)$ are the routes of $ {\cal R}_{\cal C}$, and there is an edge between two vertices if and only if there is a common arc between the two routes in $ {\cal R}_{\cal C}$.
%       
%       Given $u$ and $v$ two vertices of the conflict graph, corresponding to two routes colliding in $ {\cal R}_{\cal C}$. The weight of an edge, $w(u,v)$, is the absolute value of the difference between the distance of the two routes between their respective source node and the collision point.
%       
%       A labeling $F$ of such a graph is an affectation of an integer to each vertex, such that for each vertex $u$, $f(u) \neq f(v)+w(u,v)\mod P$, where $v$ are the neighbors of $u$ in the conflict graph and $P$ our period.

      \includegraphics[scale=0.5]{Fig5.pdf}\\
       \begin{center}
      $\lambda(v,r_i) - \lambda(v,r_j)=1$ 
     \end{center}

      On the other hand if we set all $\lambda(v,r_i) - \lambda(v,r_j)=P$, there is no $P$-periodic affectation if $P<c$.

      \includegraphics[scale=0.5]{Fig6.pdf}\\
       \begin{center}
      $\lambda(v,r_i) - \lambda(v,r_j)=2$

      Here for P=2, there is no $P$-periodic affectation.
      \end{center}

      Therefore if we choose and odd value for $P$ and $c=P+1$, if there is no $P$-periodic affectation but modulo $2$ all $\lambda(v,r_i) - \lambda(v,r_j)$
      are equal to one thus we have a $2$-periodic affectation.

   \subsection{Problems}

@@

    For each arc $(u,v) \in A$, we denote by ${\rho}(u,v)$ the subset of routes of $\cal{R}$  containing $(u,v)$.
    We define the load of an arc $(u,v)$ as the number of routes that use this arc thus : $load(u,v) = |\rho(u,v)|$.

@@

    Let $\phi$ be an edge coloring with $k$ colors of $G$. We can build a $k$ periodic affectation
    by assigning to the source $s_{u,v}$ of each route an offset  of $\phi(s_{u,v})$. Indeed, 
    if two routes $r_1$ and $r_2$ share the same edge, say $(v_1,v_2)$ then they represent two edges $e_1$ and $e_2$ of $G$ incident  
    to the vertex $v$. Therefore $\lambda(v_1,r_1) = \phi(e_1) \mod k$ because the delays of the edges before $v_1$ sum to $d(d+1)$ or 
    $2(d(d+1))$ which are equal to $0$ modulo $k$ since $k=d$ or $k=d+1$. Thus $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k = \phi(e_1) - \phi(e_2) \mod k$
    and $\lambda(v_1,r_1) - \lambda(v_1,r_2) \mod k > 0$ since $\phi(e_1) \neq \phi(e_2) $.

    Now consider a $k$-periodic affectation of $\rho$. For each $(u,v)$ in $G$, we define $\phi(u,v)$ to be the offset of the route
    beginning at $s_{u,v}$. For the same reasons as in the last paragraph, $\phi$ is an edge coloring with $k$ colors.

  Therefore if we can approximate the value of PRA  within a factor $f$,
    we could approximate the minimal number of colors needed to color a graph within a fator $f$, 
    by doing the previous reduction for all possible $k$. The proof follows from the hardness of approximability
    of finding a minimal coloring~\cite{zuckerman2006linear}.
    \end{proof}

@@

      \Edge(1)(2)
      \Edge(1)(3)
    \node (1) at (-3,4){\Huge $\rightarrow$};

    \node (2) at (-7,-2){\Huge G};
    \node (3) at (10,-2){\Huge H};
    \end{tikzpicture}

@@

	\IF{$P1[j]$ is free AND $P2[j+\lambda(r_i)]$ is free}
